Effects of bariatric surger and weight loss on resting-state functional connectivity

### 2020-11-30 draft_rsfmri.Rmd
few updates

# [ ] Introduction
# [ ] Discussion
# [ ] hervorheben, was von Präregistrierung abweicht
# [ ] brain images mit nilearn plotting tools einbinden
# [x] Figure zu weight loss
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines
# [ ] SPM model comparison

@@

# load packages
library(plyr)
library(dplyr)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(patchwork) # API for sequentially building up a plot (similar to gridExtra and cowplot)
#library(cowplot)
library(RColorBrewer)
library(psych)
#library(lsr) #

#library(wesanderson) # colour palette
#library(haven)

@@

<!-- saliency and reward -->

Studies concerning such processes following a surgical intervention are inconclusive.

@@

<!-- mixed effect model -->
Due to the limitation of the traditional ANOVA framework (with respect to the spherity assumption, handling missing data, handling continuous data), often more modern models such as mixed-effect models and marginal models are recommended [@Chen_2013;@Guillaume_2014;@McFarquhar_2019].
@McFarquhar_2019 demonstrated that specifying complex multi-level models and deriving the correct contrast weights with standard neuroimaging software packages such as SPM and FSL can be quite tedious and complicated if done appropriately. However, <!-- to rule out gross missspecification in the SwE model,  -->for the purpose of comparison, we re-ran the analysis for the group-time-interaction with age and sex as nuisance covariates.
<!-- (FD is time-varying... schwierig) with a simplified model without nuisance covariates in SPM12. We opted for a simplified model because different nuisance covariates, time-invariant or time-varying, create additional complications. -->
An advantage of the group-time interaction in our model is that the $F$-ratio does not require partitioning the error and includes only factors and time-invariant nuisance convariates. The model was set up as flexible factorial design with factors "subject", "group", and "time".

Differences may arise due to adjustments to non-spherity, but to rule out any further differences due to correction procedure, both models were evaluated with an uncorrected $p < 0.01$. Estimation was carried out via restricted maximum likelihood for $166$ voxels to correct for non-spherity. Concernes about comparability have been expressed with other toolboxed have been expressed elsewhere [@McFarquhar_2019].

Estimates retrieved with the Sandwich estimator ... comparable with 
In both models, the retrieved estimates between subjects was modeled and therefore ...

Opposed to flexible factorial models for analysis of variance, where each individual is modelled separately, models are parsimonious and preserve more degrees of freedom. Furthermore,

>>>>

# [ ] Evaluate SPM model comparison (more activation in SPM..)
# [ ] Introduction
# [ ] Discussion
# [ ] hervorheben, was von Präregistrierung abweicht
# [ ] brain images mit nilearn plotting tools einbinden
# [x] Figure zu weight loss
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines

@@

# load packages
library(plyr)
library(dplyr)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(patchwork) # API for sequentially building up a plot (similar to gridExtra and cowplot)
#library(cowplot)
library(RColorBrewer)
library(psych)
#library(lsr) 
#library(wesanderson) # colour palette
#library(haven)

@@

s concerning such processes following a surgical intervention are inconclusive.

@@

<!-- mixed effect model -->
Due to the limitation of the traditional ANOVA framework (with respect to the spherity assumption, handling missing data, handling continuous data), it is often recommended to use modern models such as mixed-effect models and marginal models [@Chen_2013;@Guillaume_2014;@McFarquhar_2019].
@McFarquhar_2019 demonstrated that specifying complex multi-level models and deriving the correct contrast weights with standard neuroimaging software packages such as SPM and FSL can be quite tedious and complicated if done appropriately. However, <!-- to rule out gross missspecification in the SwE model,  -->for the purpose of comparison, we re-ran the analysis for the group-time-interaction with age and sex as nuisance covariates.
<!-- (FD is time-varying... schwierig) with a simplified model without nuisance covariates in SPM12. We opted for a simplified model because different nuisance covariates, time-invariant or time-varying, create additional complications. -->
An advantage of the group-time interaction in our model is that the $F$-ratio does not require partitioning the error and includes only factors and time-invariant nuisance convariates. The model was set up as flexible factorial design with factors "subject", "group", and "time" assuming unequal group variances.
<!-- vastly different - different implicit masks? -->
Differences could be attributed to different corrections for non-spherity and assumptions on voxel covariance structures. Detailed comparisons between SPM12, SwE, and other software packages have been described elsewhere [@McFarquhar_2016].
<!-- conclusion??? -->
Opposed to flexible factorial models, where each individual is modelled separately, models are parsimonious and preserve more degrees of freedom.
